---
title: "Sentiment Analysis of Ted Talks"
author: "Blain Morin"
date: "November 8, 2017"
output: html_document
---

## Background

TED Talks is a popular conference that coveres a broad range scientific, cultural, and academic topics. According to wikipedia, TED Talks lectures (which are free to watch online), have been streamed over a billion times. 

Using data obtained from kaggle.com (https://www.kaggle.com/rounakbanik/ted-talks), we can use the tidytext R package to perform sentiment analysis on the TED Talk transcripts. The data also contain 17 other variables such as time filmed, tags, ratings, and user views. 

### Question 1: Which talks had the highest proportion of positive words?

```{r}
source("b01_check_install.R")
source("b02_import_clean_data.R")

```

```{r}

transcripts_clean = transcripts_clean %>%
  group_by(name) %>%
  mutate(wordcount = n()) %>%
  ungroup()

transcripts_bing %>%
  filter(sentiment == "positive") %>%
  count(name, sentiment, wordcount) %>%
  mutate(positive_p = n / wordcount) %>%
  arrange(desc(positive_p)) %>%
  top_n(20)

```
