---
title: "Text Analyis"
output: github_document
---




# Your mission

Perform text analysis.

## Okay, I need more information

Perform sentiment analysis or topic modeling using text analysis methods as demonstrated in the pre-class work and in the readings.

## Okay, I need even more information.

Do the above. Can't think of a data source?

- `gutenbergr`
- `AssociatedPress` from the `topicmodels` package
- `NYTimes` or `USCongress` from the `RTextTools` package
- Harry Potter Complete 7 Books text
```{r}
install.packages("devtools")
```
```{r}
devtools::install_github("bradleyboehmke/harrypotter")
```

- [State of the Union speeches](https://pradeepadhokshaja.wordpress.com/2017/03/31/scraping-the-web-for-presdential-inaugural-addresses-using-rvest/)
- Scrape tweets using [`twitteR`](https://www.credera.com/blog/business-intelligence/twitter-analytics-using-r-part-1-extract-tweets/)

Analyze the text for sentiment OR topic. **You do not need to do both**. The datacamp courses and [Tidy Text Mining with R](http://tidytextmining.com/) are good starting points for templates to perform this type of analysis, but feel free to *expand beyond these examples*.

# Timelines and Task


We will spend the next 2 weeks working on analyzing textual data in R. You will do the following:

- Start with some text based data.
- Clean data and prepare it for analysis
- Ask questions about the data
- Answer these questions with the data using tables and graphics
- Each group member must have their own unique question that they code the answer for. 
```{r}
library(stringr)
library(tidytext)
library(dplyr)
```
```{r}
stone=harrypotter::philosophers_stone
str_length(stone)
```
```{r}
text_df<-data_frame(line=1:17,text=stone)
stone_df<-text_df%>%unnest_tokens(word,text)
```
```{r}
tidy_stone<-stone_df%>%group_by(word)%>%anti_join(stop_words)%>%count(sort=T)%>%rename(freq=n)%>%ungroup()  ##remove stop word like "the","of".
```
```{r}
library(ggplot2)
tidy_stone%>%filter(freq>100)%>%mutate(word=reorder(word,freq))%>%ggplot(aes(word,freq))+geom_col()+xlab(NULL)+coord_flip()
##reorder means converts word from a character that would be plotted in alphabetical order to a factor that will be plotted in order of n.coord_flip flips the coordinates.geom_col makes the barchart.
```
```{r}
stone_sentiment <- stone_df%>%inner_join(get_sentiments("bing"))
stone_sentiment_count<-stone_sentiment%>%group_by(word)%>%count%>%ungroup()
stone_sentiment_count%>%filter(n>20)%>%mutate(word=reorder(word,n))%>%ggplot(aes(word,n))+geom_col()+xlab(NULL)+coord_flip()
```